Dynastic Extinctions and Urban Economic Development: \\Evidence from the Holy Roman Empire\footnote{I thank Davide Cantoni, Matthias Weigand, and my RA colleagues at the Chair of Economic History for helpful comments and feedback.}

### 2023-06-07 paper/paper.tex
#22 add handbook articles and snippets

% one paragraph to get the reader from where he stands, to understanding and caring about the research question.

>>>>

The state system of early modern Europe was fraught with conflict.

This paper studies a different interaction between conflict and growth. I study how conflict affected the institutional quality of states. In particular, I investigate whether wars and conflict served as a selection mechanism - whether the constant competition caused better states to grow and worse states to shrink and eventually disappear.

These ideas are not new -

Institutional factors that benefit a state's economy also benefit a state's ability to win conflicts with others.

While frequent wars brought devastation over the people and destruction to property, \cite{malthus1798} and others after him have argued, frequent wars may have kept population in check, leading to higher land-labour ratios and therefore a higher level of income per capita. \cite{voigtlnder2013} argue that the relative wealth of Europe after 1350 can be explained by a feedback loop centered on this Malthusian mechanism: after the huge loss of life caused by the Black Death, which served as a catalyst, taxable incomes rose, which made rulers richer, which allowed them to afford more wars, which in turn kept population in check.
